Experiment 2

### 2018-03-13 analysis_code/agents_table.Rmd
new results

dat <- read.csv(file=paste(WORKING_PATH, "/results/free_obs_raw_results/free_obs_experiment_raw_results_4.csv", sep=""))
p1_algs <- as.list(unique(dat['P1.Alg']))$P1.Alg
p2_algs <- as.list(unique(dat['P2.Alg']))$P2.Alg
agent_algs <- as.list(unique(dat['Agent.Alg']))$Agent.Alg
time_horizons <-  as.list(unique(dat['Time.Horizon']))$Time.Horizon
priors <- as.list(unique(dat['Prior']))$Prior
EXPERIMENT_1_CV_HIGH <- 156.71410383 #chisquared critical values for 124 degrees of freedom
EXPERIMENT_1_CV_LOW <- 95.07008897

EXPERIMENT_2_CV_HIGH <- 128.42198864
EXPERIMENT_2_CV_LOW <- 73.36108019

@@

alg_pairs <- c("ThompsonSampling", "DynamicEpsilonGreedy", "ThompsonSampling", "DynamicGreedy", "DynamicGreedy", "DynamicEpsilonGreedy")
print("Reported means are for principal 1 which is the first algorithm listed in the pair for each column<br>")
print("In each cell, first line is mean, second line is variance, third line is % of the time that market share > 0.1 or market share < 0.9")
library(xtable)
for (prior in priors) {
  for (j in 1:length(time_horizons)) {
    results <- matrix(nrow=length(agent_algs), ncol=length(algs))
    colnames(results) <- c(paste(concise_alg_rep(alg_pairs[1]), concise_alg_rep(alg_pairs[2]), sep=" vs "), paste(concise_alg_rep(alg_pairs[3]), concise_alg_rep(alg_pairs[4]), sep=" vs "), paste(concise_alg_rep(alg_pairs[5]), concise_alg_rep(alg_pairs[6]), sep=" vs "))
    rownames(results) <- get_agent_rep(agent_algs)
    for (i in 1:length(agent_algs)) {
      agent_alg <- agent_algs[i]
      time <- time_horizons[j]
      for (k in 1:length(alg_pairs)) {
        if (k %% 2 == 0) { next }
          p1alg = alg_pairs[k]
          p2alg = alg_pairs[k+1]
          filtered_dat <- filter(dat, P1.Alg == p1alg & P2.Alg == p2alg & Memory.Size == 100 & Prior == prior & Agent.Alg == agent_alg & Time.Horizon == time)
          if (nrow(filtered_dat) == 0) {
            next
          }
          share <- filtered_dat$Market.Share.for.P1
          test <- t.test(share)
          cin <- signif(test$conf.int[2] - mean(share), digits=2)
          shares <- sum(share >= (1 - ZERO_ONE_CUTOFF) | share <= ZERO_ONE_CUTOFF, na.rm=TRUE) / nrow(filtered_dat)
          shares_percent <- signif(shares * 100, digits=2)
          lower_var <- signif((length(share) - 1) * var(share) / EXPERIMENT_1_CV_HIGH, digits=2)
          high_var <- signif((length(share) - 1) * var(share) / EXPERIMENT_1_CV_LOW, digits=2)
          results[i, (k+1)/2] <- paste("<b>",signif(mean(share), digits=2), "</b> +/-", cin, "<br>", signif(var(share), digits=2), paste("(", lower_var, ", ", high_var, ")", sep=""), "<br>", "Extreme Shares:", shares_percent, "%")
        }
      }
      tab <-xtable(results, caption=paste("Results for", time, prior))
      print(tab, type="html")
  }
  print('<br><br><br><br><br><br>')
  }

>>>>

#dat <- read.csv(file=paste(WORKING_PATH, "/results/free_obs_raw_results/free_obs_experiment_tournament_raw_results.csv", sep=""))
dat <- read.csv(file=paste(WORKING_PATH, "/results/tournament_raw_results/full_tournament_raw_results.csv", sep=""))
p1_algs <- as.list(unique(dat['P1.Alg']))$P1.Alg
p2_algs <- as.list(unique(dat['P2.Alg']))$P2.Alg
agent_algs <- as.list(unique(dat['Agent.Alg']))$Agent.Alg
memory_sizes <- sort(as.list(unique(dat['Memory.Size']))$Memory.Size, decreasing=TRUE)
time_horizons <-  as.list(unique(dat['Time.Horizon']))$Time.Horizon
time_horizons <- c(1000)
priors <- as.list(unique(dat['Prior']))$Prior

@@

alg_pairs <- c("ThompsonSampling", "DynamicEpsilonGreedy", "ThompsonSampling", "DynamicGreedy", "DynamicGreedy", "DynamicEpsilonGreedy", "ThompsonSampling", "ThompsonSampling", "DynamicEpsilonGreedy", "DynamicEpsilonGreedy", "DynamicGreedy", "DynamicGreedy")
#print("Reported means are for principal 1 which is the first algorithm listed in the pair for each column<br>")
#print("In each cell, first line is mean, second line is variance, third line is % of the time that market share > 0.1 or market share < 0.9")
library(xtable)
for (memory in memory_sizes) {
for (prior in priors) {
    for (j in 1:length(time_horizons)) {
      results <- matrix(nrow=length(agent_algs), ncol=(length(alg_pairs) / 2))
    colnames(results) <- c(paste(concise_alg_rep(alg_pairs[1]), concise_alg_rep(alg_pairs[2]), sep=" vs "), paste(concise_alg_rep(alg_pairs[3]), concise_alg_rep(alg_pairs[4]), sep=" vs "), paste(concise_alg_rep(alg_pairs[5]), concise_alg_rep(alg_pairs[6]), sep=" vs "), paste(concise_alg_rep(alg_pairs[7]), concise_alg_rep(alg_pairs[8]), sep=" vs "), paste(concise_alg_rep(alg_pairs[9]), concise_alg_rep(alg_pairs[10]), sep=" vs "), paste(concise_alg_rep(alg_pairs[11]), concise_alg_rep(alg_pairs[12]), sep=" vs "))
    rownames(results) <- get_agent_rep(agent_algs)
    for (i in 1:length(agent_algs)) {
      agent_alg <- agent_algs[i]
      time <- time_horizons[j]
      for (k in 1:length(alg_pairs)) {
        if (k %% 2 == 0) { next }
          p1alg = alg_pairs[k]
          p2alg = alg_pairs[k+1]
          filtered_dat <- filter(dat, P1.Alg == p1alg & P2.Alg == p2alg & Memory.Size == memory & Prior == prior & Agent.Alg == agent_alg & Time.Horizon == time)
          if (nrow(filtered_dat) == 0) {
            next
          }
          share <- filtered_dat$Market.Share.for.P1
          test <- t.test(share)
          cin <- signif(test$conf.int[2] - mean(share), digits=1)
          shares <- sum(share >= (1 - ZERO_ONE_CUTOFF) | share <= ZERO_ONE_CUTOFF, na.rm=TRUE) / nrow(filtered_dat)
          shares_percent <- signif(shares * 100, digits=2)
          cv_high <- qchisq(.975, df=length(share) - 1)
          cv_low <- qchisq(.025, df=length(share) - 1)
          lower_var <- signif((length(share) - 1) * var(share) / cv_high, digits=1)
          high_var <- signif((length(share) - 1) * var(share) / cv_low, digits=1)
          results[i, (k+1)/2] <- paste("<b>",signif(mean(share), digits=2), "</b> +/-", cin, "<br>Var:", signif(var(share), digits=2), "<br>Share:", shares_percent, "%")
      }
    }
      tab <-xtable(results, caption=paste("Results for", "t=",time, prior, "Memory=", memory))
      print(tab, type="html")
  }
  }
}

### 2018-03-13 analysis_code/tournament_table.Rmd
new results

dat <- read.csv(file=paste(WORKING_PATH, "/results/free_obs_raw_results/free_obs_experiment_raw_results.csv", sep=""))
p1_algs <- as.list(unique(dat['P1.Alg']))$P1.Alg
p2_algs <- as.list(unique(dat['P2.Alg']))$P2.Alg
memory_sizes <- sort(as.list(unique(dat['Memory.Size']))$Memory.Size, decreasing=TRUE)
agent_algs <- as.list(unique(dat['Agent.Alg']))$Agent.Alg
time_horizons <-  as.list(unique(dat['Time.Horizon']))$Time.Horizon
time_horizons <- c(5000, 10000, 15000)
priors <- as.list(unique(dat['Prior']))$Prior

ZERO_ONE_CUTOFF <- 0.1
algs <- c("ThompsonSampling", "DynamicEpsilonGreedy", "DynamicGreedy")
options(xtable.sanitize.text.function=identity)
options(xtable.caption.placement="top")
library(xtable)
for (j in 1:length(time_horizons)) {
  for (prior in priors) {
    for (i in 1:length(agent_algs)) {
      agent_alg <- agent_algs[i]
      print_breaks <- FALSE
        time <- time_horizons[j]
        results <- matrix(nrow=length(algs), ncol=length(algs))
        colnames(results) <- algs
        rownames(results) <- algs
        for (k in 1:length(algs)) {
          for (l in 1:length(algs)) {
            p1alg = algs[k]
            p2alg = algs[l]
            filtered_dat <- filter(dat, P1.Alg == p1alg & P2.Alg == p2alg & Memory.Size == 100 & Prior == prior & Agent.Alg == agent_alg & Time.Horizon == time)
            if (nrow(filtered_dat) == 0) {
              if (p1alg == p2alg) { print_breaks <- TRUE }
              next
            }
            share <- filtered_dat$Market.Share.for.P1
            test <- t.test(share)
            cin <- signif(test$conf.int[2] - mean(share), digits=2)
            shares <- sum(share >= (1 - ZERO_ONE_CUTOFF) | share <= ZERO_ONE_CUTOFF, na.rm=TRUE) / nrow(filtered_dat)
            cv_high <- qchisq(.975, df=length(share) - 1)
            cv_low <- qchisq(.025, df=length(share) - 1)
            lower_var <- signif((length(share) - 1) * var(share) / cv_high, digits=2)
            high_var <- signif((length(share) - 1) * var(share) / cv_low, digits=2)
            results[k, l] <- paste("<b>", signif(mean(share), digits=2), "</b> +/-", cin, "<br>", signif(var(share), digits=2), paste("(", lower_var, ", ", high_var, ")", sep=""), "<br>", "Extreme Shares:", shares)
          }
        }
        tab <-xtable(results, caption=paste("Results for", agent_alg, "t =", time, prior))
        print(tab, type="html")
        if (print_breaks) { print("<br>") }
      }
    }
  }

>>>>

dat <- read.csv(file=paste(WORKING_PATH, "/results/tournament_raw_results/full_tournament_raw_results.csv", sep=""))
#dat <- read.csv(file=paste(WORKING_PATH, "/results/free_obs_raw_results/free_obs_experiment_tournament_raw_results.csv", sep=""))
p1_algs <- as.list(unique(dat['P1.Alg']))$P1.Alg
p2_algs <- as.list(unique(dat['P2.Alg']))$P2.Alg
memory_sizes <- sort(as.list(unique(dat['Memory.Size']))$Memory.Size, decreasing=TRUE)
agent_algs <- as.list(unique(dat['Agent.Alg']))$Agent.Alg
time_horizons <-  as.list(unique(dat['Time.Horizon']))$Time.Horizon
time_horizons <- c(1000)
priors <- as.list(unique(dat['Prior']))$Prior

ZERO_ONE_CUTOFF <- 0.1
algs <- c("ThompsonSampling", "DynamicEpsilonGreedy", "DynamicGreedy")
options(xtable.sanitize.text.function=identity)
options(xtable.caption.placement="top")
library(xtable)
for (j in 1:length(time_horizons)) {
  for (prior in priors) {
    for (i in 1:length(agent_algs)) {
      agent_alg <- agent_algs[i]
      print_breaks <- FALSE
        time <- time_horizons[j]
        results <- matrix(nrow=length(algs), ncol=length(algs))
        colnames(results) <- algs
        rownames(results) <- algs
        for (k in 1:length(algs)) {
          for (l in 1:length(algs)) {
            p1alg = algs[k]
            p2alg = algs[l]
            filtered_dat <- filter(dat, P1.Alg == p1alg & P2.Alg == p2alg & Memory.Size == 100 & Prior == prior & Agent.Alg == agent_alg & Time.Horizon == time)
            if (nrow(filtered_dat) == 0) {
              if (p1alg == p2alg) { print_breaks <- TRUE }
              next
            }
            share <- filtered_dat$Market.Share.for.P1
            test <- t.test(share)
            cin <- signif(test$conf.int[2] - mean(share), digits=2)
            shares <- sum(share >= (1 - ZERO_ONE_CUTOFF) | share <= ZERO_ONE_CUTOFF, na.rm=TRUE) / nrow(filtered_dat)
            cv_high <- qchisq(.975, df=length(share) - 1)
            cv_low <- qchisq(.025, df=length(share) - 1)
            lower_var <- signif((length(share) - 1) * var(share) / cv_high, digits=2)
            high_var <- signif((length(share) - 1) * var(share) / cv_low, digits=2)
            results[k, l] <- paste("<b>", signif(mean(share), digits=2), "</b> +/-", cin, "<br>", signif(var(share), digits=2), paste("(", lower_var, ", ", high_var, ")", sep=""), "<br>", "Extreme Shares:", 100*signif(shares, digits=2), "%")
          }
        }
        tab <-xtable(results, caption=paste("Results for", agent_alg, "t =", time, prior))
        print(tab, type="html")
        if (print_breaks) { print("<br>") }
      }
    }
  }

### 2018-03-13 experiment_1/experiment_1.tex
new results

\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[hidelinks]{hyperref}
\usepackage{float}
\usepackage{amsfonts}
\usepackage{algorithm,algpseudocode}

@@

Considered $K = 3$, $T = 5005$. Report statistics at $t = 1000, 3000, 5000$ \\
\textbf{The Bandit priors that were considered}:
\begin{itemize}
\item Uniform: Draw the mean rewards for the arms from [0.25, 0.75]
\item ``HeavyTail": We took the mean rewards to be randomly drawn from Beta($\alpha=0.6,\beta=0.6$). With this distribution it was likely to have arms that were at the extremes (close to 1 and close to 0) but also some of the arms with intermediate value means.
\item Needle-in-haystack
\begin{enumerate}
\item Medium - 9 arms with mean 0.50, 1 arm with mean 0.55 (+ 0.05)
\item High - 9 arms with mean 0.50, 1 arm with mean 0.70 (+ 0.20)
\end{enumerate}
\end{itemize}
\textbf{Algorithms considered}:
\begin{enumerate}
\item ThompsonSampling with priors of $Beta(1, 1)$ for every arm.
\item DynamicGreedy with priors of $Beta(1, 1)$ for every arm
\item Bayesian Dynamic $\epsilon$-greedy with priors of $Beta(1, 1)$ for every arm and $\epsilon=0.05$
\end{enumerate}
\textbf{Agent Algorithms considered}:
\begin{enumerate}
\item HardMax
\item HardMaxWithRandom
\item SoftMax
\end{enumerate}
\textbf{Memory Sizes}
\begin{enumerate}
\item 10
\item 25
\item 100
\end{enumerate}
\pagebreak
\textbf{Simulation Procedure}
\begin{algorithm}
\begin{algorithmic}[1]
\For{Each prior $p$}
	\For{Each agent algorithm $agent_alg$}
		\For{Each principal algorithm pair $principal_alg1$, $principal_alg2$}
			\For{Each simulation $i$}
				\State Generate true distribution from $p$ (except for needle-in-		haystack, just use $p$ itself)
				\State Run simulation for T periods
			\EndFor
		\EndFor
	\EndFor
\EndFor
\end{algorithmic}
\end{algorithm}

\pagebreak
\section*{Results}

One thing which is ambiguous to define is the regret value to use when a principal never gets chosen in a given simulation. When calculating any of the aggregate regret statistics we drop these simulations, but we do record how many rounds have an undefined regret. \\
\vspace{1cm}

First, we'll restrict focus to $t = 5000$ and look at the performance of ThompsonSampling. Note that the y axis here represents the market share that the ThompsonSampling principal gets.
\vspace{0.5cm}
Performance of ThompsonSampling vs DynamicGreedy and DynamicEpsilonGreedy across all agent models, memory sizes, and priors: \\
\includegraphics[scale=0.75]{ts_perf_dg} \\
\includegraphics[scale=0.75]{ts_perf_deg} \\

Now, looking across different memory sizes for each agent model (still using each prior): \\
\textbf{HardMax} \\
\includegraphics[scale=0.75]{hm_ts_deg} \\
\includegraphics[scale=0.75]{hm_ts_dg} \\

\pagebreak
\textbf{HardMaxWithRandom} \\
\includegraphics[scale=0.75]{hmr_ts_deg} \\
\includegraphics[scale=0.75]{hmr_ts_dg} \\

\pagebreak
\textbf{SoftMax} \\
\includegraphics[scale=0.75]{sm_ts_deg} \\
\includegraphics[scale=0.75]{sm_ts_dg} \\

\pagebreak
We'll now look fix memory size to be 100 and look at the performance across priors.\\
\textbf{HardMax} \\
\includegraphics[scale=0.75]{hm_ts_deg_prior} \\
\includegraphics[scale=0.75]{hm_ts_dg_prior} \\

\pagebreak
\textbf{HardMaxWithRandom} \\
\includegraphics[scale=0.75]{hmr_ts_deg_prior} \\
\includegraphics[scale=0.75]{hmr_ts_dg_prior} \\

\pagebreak
\textbf{SoftMax} \\
\includegraphics[scale=0.75]{sm_ts_deg_prior} \\
\includegraphics[scale=0.75]{sm_ts_dg_prior} \\

>>>>

\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[hidelinks]{hyperref}
\usepackage{float}
\usepackage{amsfonts}
\usepackage{algorithm,algpseudocode}
\usepackage{pdfpages}

@@

Considered $K = 3$, $T = 1001$, $N = 1200$. Report statistics at $t = 1000$ \\
\textbf{The Bandit priors that were considered}:
\begin{itemize}
\item Uniform: Draw the mean rewards for the arms from [0.25, 0.75]
\item ``HeavyTail": We took the mean rewards to be randomly drawn from Beta($\alpha=0.6,\beta=0.6$). With this distribution it was likely to have arms that were at the extremes (close to 1 and close to 0) but also some of the arms with intermediate value means.
\item Needle-in-haystack
\begin{enumerate}
\item High - 2 arms with mean 0.50, 1 arm with mean 0.70 (+ 0.20)
\end{enumerate}
\end{itemize}
\textbf{Algorithms considered}:
\begin{enumerate}
\item ThompsonSampling with priors of $Beta(1, 1)$ for every arm.
\item DynamicGreedy with priors of $Beta(1, 1)$ for every arm
\item Bayesian Dynamic $\epsilon$-greedy with priors of $Beta(1, 1)$ for every arm and $\epsilon=0.05$
\end{enumerate}
\textbf{Agent Algorithms considered}:
\begin{enumerate}
\item HardMax
\item HardMaxWithRandom
\item SoftMax ($\alpha = 30$)
\end{enumerate}
\textbf{Memory Sizes}
\begin{enumerate}
\item 100
\end{enumerate}
\pagebreak
\textbf{Simulation Procedure}
\begin{algorithm}
\begin{algorithmic}[1]
\For{Each prior $p$}
\State Generate true distribution from $p$ (except for needle-in-haystack, just use $p$ itself)
\State Generate $T \times K$ realizations for the arms 
	\For{Each agent algorithm $agent alg$}
		\For{Each principal algorithm pair $principalalg1$, $principalalg2$}
			\For{$N$ simulations}

				\State Give the agents 5 observations from each principal
				\State Run simulation for T periods
			\EndFor
		\EndFor
	\EndFor
\EndFor
\end{algorithmic}
\end{algorithm}

\section*{Results}
All results are reported for memory size = 100. \\
\vspace{0.25cm}

The rows represent the agent algorithms (defined as above). The columns represent principal 1 vs principal 2 (e.g. TS vs DG means Thompson Sampling is principal 1 and Dynamic Greedy is principal 2).  \\
\vspace{0.1cm}

Within each cell, the following data are presented: \\

\begin{enumerate}
\item The first row displays the sample mean market share for principal 1 as well as a 95\% confidence band of the mean.

\item The second row displays the sample variance of the market share and in parentheses are 95 \% confidence bands for the variance.

\item The third row displays the \% of simulations that resulted in ``extreme" market shares. Extreme market shares are defined as being simulations were one of the principals (either principal 1 or 2) ended up with 90\% or more of the market.
\end{enumerate}
\includepdf[pages={-}]{agents_table}
Comments: Almost everything is just a 50-50 split!
\begin{enumerate}
\item Almost all of the same algorithms pitted against each other ended with getting a 50/50 market share. This seems to be a good sanity check.
\item Strange things: focus on TS vs DEG (Heavy Tail). DEG wins for HM and HMR, but TS wins for SM. This seems weird? TS also seems to lose on HMR with Uniform prior.
\item Why does DynamicGreedy do so well on the HeavyTail prior? Does this make sense?
\end{enumerate}

### 2018-03-13 experiment_2/experiment_2.tex
updates
new results

\section*{Differences from Experiment 1}

The only difference between this experiment and experiment 1 is that we give principal 2 a ``headstart" in the sense of letting them be the only firm in the market for the first 1000 periods. Thus, the principals are effectively given 1000 free observations for learning and the agents are given 1000 free observations in order to form a reputation score for principal 2. The question this simulation then attempts to answer is if \textit{information advantage} can be viewed as a barrier to entry. Namely, it attempts to begin to answer if the first mover advantage manifests itself in this model by giving the incumbent firm a better prior than any entrants (who we assume come in with only ``fake" priors). Under what assumptions about the agent rationality (response functions or memory sizes) and what algorithms do we see the entering firm able to gain any market share?
\section*{Simulation Details}

Considered $K = 3$, $T = 5005$, $N = 60$. Report statistics at $t = 1000, 3000, 5000$ \\
\textbf{The Bandit priors that were considered}:
\begin{itemize}
\item Uniform: Draw the mean rewards for the arms from [0.25, 0.75]
\item ``HeavyTail": We took the mean rewards to be randomly drawn from Beta($\alpha=0.6,\beta=0.6$). With this distribution it was likely to have arms that were at the extremes (close to 1 and close to 0) but also some of the arms with intermediate value means.
\item Needle-in-haystack
\begin{enumerate}
\item Medium - 9 arms with mean 0.50, 1 arm with mean 0.55 (+ 0.05)
\item High - 9 arms with mean 0.50, 1 arm with mean 0.70 (+ 0.20)
\end{enumerate}
\end{itemize}
\textbf{Algorithms considered}:
\begin{enumerate}
\item ThompsonSampling with priors of $Beta(1, 1)$ for every arm.
\item DynamicGreedy with priors of $Beta(1, 1)$ for every arm
\item Bayesian Dynamic $\epsilon$-greedy with priors of $Beta(1, 1)$ for every arm and $\epsilon=0.05$
\end{enumerate}
\textbf{Agent Algorithms considered}:
\begin{enumerate}
\item HardMax
\item HardMaxWithRandom
\item SoftMax
\end{enumerate}
\textbf{Memory Sizes}
\begin{enumerate}
\item 10
\item 25
\item 100
\end{enumerate}

The simulation procedure is the only thing that has changed compared to Experiment 1:
\textbf{Simulation Procedure}
\begin{algorithm}
\begin{algorithmic}[1]
\For{Each prior $p$}
	\For{Each agent algorithm $agent alg$}
		\For{Each principal algorithm pair $principalalg1$, $principalalg2$}
			\For{$N$ simulations}
				\State Generate true distribution from $p$ (except for needle-in-haystack, just use $p$ itself)
				\State Give the agents 5 observations from each principal
				\State Give principal 2 1000 free observations (and give the agents this information too)
				\State Run simulation for T periods
			\EndFor
		\EndFor
	\EndFor
\EndFor
\end{algorithmic}
\end{algorithm}

\pagebreak
\section*{Results}
\textbf{HardMax} \\
\includegraphics[scale=0.9]{hm_ts_dg_memory_5000} \\ \includegraphics[scale=0.9]{hm_ts_deg_memory_5000} \\
The main interesting result here is that for ThompsonSampling vs DEG, with low memory sizes we have that ThompsonSampling almost catches up to DEG, but as we increase memory size TS gets almost no market share! Should re-run this experiment with higher N to validate this.

\pagebreak
\textbf{HardMaxWithRandom}  \\
\includegraphics[scale=0.9]{hmr_ts_dg_memory_5000} \\ \includegraphics[scale=0.9]{hmr_ts_deg_memory_5000}

\pagebreak
\textbf{SoftMax} \\
\includegraphics[scale=0.9]{sm_ts_dg_memory_5000} \\ \includegraphics[scale=0.9]{sm_ts_deg_memory_5000}

\pagebreak
Zooming in on the HardMax results and looking at them over time we get (for memory = 25): \\
\includegraphics[scale=0.9]{hm_ts_deg_25_timehorizon} \\ \includegraphics[scale=0.9]{hm_ts_dg_25_timehorizon}

\pagebreak
\textbf{Memory = 100} \\
Take note of the scale on the y-axis on this graph. \\
\includegraphics[scale=0.9]{hm_ts_deg_100_timehorizon} \\ \includegraphics[scale=0.9]{hm_ts_dg_100_timehorizon}

>>>>

\section*{Simulation Details}

Considered $K = 3$, $T = 1001$, $N = 500$. Report statistics at $t = 1000$ \\
\textbf{The Bandit priors that were considered}:
\begin{itemize}
\item Uniform: Draw the mean rewards for the arms from [0.25, 0.75]
\item ``HeavyTail": We took the mean rewards to be randomly drawn from Beta($\alpha=0.6,\beta=0.6$). With this distribution it was likely to have arms that were at the extremes (close to 1 and close to 0) but also some of the arms with intermediate value means.
\item Needle-in-haystack
\begin{enumerate}
\item High - 2 arms with mean 0.50, 1 arm with mean 0.70 (+ 0.20)
\end{enumerate}
\end{itemize}
\textbf{Algorithms considered}:
\begin{enumerate}
\item ThompsonSampling with priors of $Beta(1, 1)$ for every arm.
\item DynamicGreedy with priors of $Beta(1, 1)$ for every arm
\item Bayesian Dynamic $\epsilon$-greedy with priors of $Beta(1, 1)$ for every arm and $\epsilon=0.05$
\end{enumerate}
\textbf{Agent Algorithms considered}:
\begin{enumerate}
\item HardMax
\item HardMaxWithRandom
\item SoftMax ($\alpha = 10$)
\end{enumerate}
\textbf{Memory Sizes}
\begin{enumerate}
\item 100
\end{enumerate}
\pagebreak
\textbf{Simulation Procedure}
\begin{algorithm}
\begin{algorithmic}[1]
\For{Each prior $p$}
\State Generate true distribution from $p$ (except for needle-in-haystack, just use $p$ itself)
\State Generate $T \times K$ realizations for the arms 
	\For{Each agent algorithm $agent alg$}
		\For{Each principal algorithm pair $principalalg1$, $principalalg2$}
			\For{$N$ simulations}

				\State Give the agents 5 observations from each principal
				\State Give principal 2 200 free observations (the agents also get these observations)
				\State Run simulation for T periods
			\EndFor
		\EndFor
	\EndFor
\EndFor
\end{algorithmic}
\end{algorithm}

\section*{Results}
All results are reported for memory size = 100. \\
\vspace{0.25cm}

The rows represent Principal 1 and the columns represent Principal 2. Thus, the cell (1, 2) represents principal 1 playing Thompson Sampling and principal 2 playing DynamicEpsilonGreedy. In this experiment remember that principal 2 gets 200 free observations.  \\
\vspace{0.1cm}

Within each cell, the following data are presented: \\

\begin{enumerate}
\item The first row displays the sample mean market share for principal 1 as well as a 95\% confidence band of the mean.

\item The second row displays the sample variance of the market share and in parentheses are 95 \% confidence bands for the variance.

\item The third row displays the \% of simulations that resulted in ``extreme" market shares. Extreme market shares are defined as being simulations were one of the principals (either principal 1 or 2) ended up with 90\% or more of the market.
\end{enumerate}
\includepdf[pages={-}]{tournament_table}

Comments: The story I seem to get from this is (roughly) that the worse the algorithm that the incumbent plays is, the better the entrant will do. However, in order for the entrant to do as well as possible, the entrant should play a worse algorithm! This seems counterintuitive, it means that the worst case for the entrant is when we're both playing ThompsonSampling and the best case for the entrant is when we're both playing DynamicGreedy.
